\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{geometry}
\usepackage{multicol}
\usepackage{xcolor}
\geometry{left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm} % Set the page margins
\setlength{\parindent}{0pt} % Removes paragraph indentation
\linespread{1.01} % Adjust line spacing as necessary


% Define the publication command
\newcommand{\publication}[7]{
  \begin{itemize}[leftmargin=*,labelsep=0.5em]
    \item[--] \textbf{#1} \\
    #2 \\
    \textit{Conference:} #3, #4. \\
    \textit{Description:} #5 \\
    \textit{Links:} \href{#6}{#7}
  \end{itemize}
}

% Command to print a publication if its boolean is true
\newcommand{\printPublication}[2]{
  \ifbool{#1}{
    \item[--] #2
  }{}
}

% Command to start the multicolumn list
\newcommand{\startPublicationList}{
    \vspace{-10pt}
    \begin{itemize}[leftmargin=*,labelsep=0.5em]
    \begin{multicols}{2}
}

% Command to end the multicolumn list
\renewcommand{\endPublicationList}{
    \end{multicols}
    \end{itemize}
    \vspace{-10pt}
}
\newcommand{\endPublicationList}{
    \end{multicols}
    \end{itemize}
    \vspace{-10pt}
}


\newbool{pubCurbScan}
\newbool{pubAdvancedDriverAssistance}
\newbool{pubDensityAdaptiveSampling}
\newbool{pubDiverseTrajectoryForecasting}
\newbool{pubFastPolarAttentive}
\newbool{pubSmartAnnotation}
\newbool{pubTrajformer}

% Set to 'true' to include the publication, 'false' to exclude it
\booltrue{pubCurbScan}
\booltrue{pubAdvancedDriverAssistance}
\boolfalse{pubDensityAdaptiveSampling}
\booltrue{pubDiverseTrajectoryForecasting}
\boolfalse{pubFastPolarAttentive}
\boolfalse{pubSmartAnnotation}
\boolfalse{pubTrajformer}

% Define colors
\definecolor{linkcolor}{rgb}{0, 0.2, 0.6}
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.3}

% Hyperref setup
\hypersetup{
    colorlinks = true,
    linkcolor = {linkcolor},
    urlcolor = {linkcolor}
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 }
  }
}

\newcommand{\resumeSubheading}[4]{
\item
    \begin{tabular*}{0.5\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \multicolumn{2}{ }{\textbf{#1}}  { \space #2} 
      % \textit{\small#3} & \textit{\small #4} \\
      \multicolumn{2}{ }{\parbox{0.8\linewidth}{\textit{\small#3}} }{\parbox{0.96\linewidth}{\textit{\small #4}}}
    \end{tabular*}
}
% Define the resumeSubheading command to accept four parameters
\newcommand{\resumeSubheadingexp}[4]{

  \item
    \begin{tabular*}{0.5\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} &\\  #2 
      \multicolumn{2}{ }{\parbox{0.8\linewidth}{\textit{\small#3}} }{\parbox{0.96\linewidth}{\textit{\small #4}}}
    \end{tabular*}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{0pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-8pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}




% Define the environment for the resume items list
\newenvironment{resumeItemList}{
  \begin{itemize}[leftmargin=*,labelsep=0em]
}{
  \end{itemize}
}

%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Manoj Bhat} \\ \vspace{1pt}
    \small 412-320-9716 $|$ \href{mailto:manojbhat.research@gmail.com}{\underline{manojbhat.research@gmail.com}} $|$ 
    \href{https://linkedin.com/in/bhat-manoj}{\underline{linkedin.com/in/bhat-manoj}} $|$
    \href{https://github.com/Manojbhat09}{\underline{github.com/Manojbhat09}} $|$
    \href{https://manojbhatwebsite.com}{\underline{Personal Website}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Carnegie Mellon University (CMU)}{Pittsburgh, PA} 
      {Master of Science in ME: Research in Robotics \& Vision}{May 2020}
      \resumeItemListStart
        \resumeItem{GPA: 3.8/4.0}
        \resumeItem{Courses: SLAM, Intro to Deep learning, Multimodal Machine Learning, Visual Recognition and Learning, Parallel Computing Architecture}
      \resumeItemListEnd

    \resumeSubheading
      {Manipal Institute of Technology (MiT)}{India}
      {Bachelor of Science in Mechanical – Minor in Mechatronics}{May 2018}
      \resumeItemListStart
        \resumeItem{GPA: 9.55/10.0}
        \resumeItem{Courses: ML and AI for Engineers, Linear Control Systems, Computer Vision, Bayesian-statistics, Computer Systems}
      \resumeItemListEnd
  \resumeSubHeadingListEnd



% [Add Patents and Publications section if applicable]
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheadingexp
      {Rivian | Offboard Planning, Machine Learning Engineer II} {}
      {Planning \& Simulation}{Apr 2023 – Present}
      \resumeItemListStart
        \resumeItem{Spearheaded the implementation of Wayformer, a state-of-the-art motion forecasting model, for offboard planning in AV.}
        \resumeItem{Worked with Neural Rendering Fields and Diffusion models for scenario dataset auto-generation.}
        \resumeItem{Utilized GPT4V for internal tooling and faster prototyping.}
      \resumeItemListEnd

    \resumeSubheadingexp
      {Amazon Robotics | Scout, Machine Learning Engineer II}{}
      {Perception \& Simulation}{Oct 2021 – Feb 2023}
      \resumeItemListStart
        \resumeItem{Lead design of AWS distributed system for scaling machine learning models in PyTorch \& VDDS stack.}
        \resumeItem{Improved model mAP/mIOU metrics through redesign for robot pose matching in simulator.}
      \resumeItemListEnd

    \resumeSubheadingexp
      {Qualcomm Drive | Research Software Engineer}{}
      {3D Lidar Detection, Behavior Planning \& Deep Learning}{Sept 2020 – Oct 2021}
      \resumeItemListStart
        \resumeItem{Implemented Lane Graphs \& VectorNet focusing on Lane association, trajectory prediction, and vehicle behavior.}
        \resumeItem{Developed 3D Transformer Object detection ML pipeline, improving overall performance and reducing latency.}
      \resumeItemListEnd

    \resumeSubheadingexp
      {Safe AI Lab | Software Engineer Robotics}{}
      {AI \& AV Research}{Aug 2018 – May 2020}
      \resumeItemListStart
        \resumeItem{Developed Neural network with CRF-CNN for 2D \& 3D Object detection in sensor fused data.}
        \resumeItem{Worked on Lidar-camera calibration and developed simulation scenarios in Carla Simulator.}
      \resumeItemListEnd

    \resumeSubheadingexp
      {Robert Bosch Gmbh | Software Engineer}{}
      {Computer Vision}{May 2019 – Sept 2019}
      \resumeItemListStart
        \resumeItem{Evaluated PointCNN-XCRF for region proposal in segmentation and denoising techniques.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

  %-----------PUBLICATIONS-----------

\section*{Publications \& Patents}

% \startPublicationList
% \printPublication{pubCurbScan}{
% \publication
% {CurbScan: Curb Detection and Tracking Using Multi-Sensor Fusion}
% {Iljoo Baek, Tzu-Chieh Tai, Manoj Mohan Bhat, Karun Ellango, Tarang Shah, Kamal Fuseini, Ragunathan (Raj) Rajkumar}
% {arXiv, 2020}
% {Approach for curb detection and tracking in urban environments by fusing data from sparse LiDAR, a mono camera, and ultrasonic sensors. Demonstrates over 90\% accuracy in various environments}
% {\href{https://www.youtube.com/watch?v=w5MwsdWhcy4}}{Demo Video 1}
% }


\startPublicationList
\printPublication{pubCurbScan}{
  \publication
    {CurbScan: Curb Detection and Tracking Using Multi-Sensor Fusion}
    {Iljoo Baek, Tzu-Chieh Tai, Manoj Mohan Bhat, Karun Ellango, Tarang Shah, Kamal Fuseini, Ragunathan (Raj) Rajkumar}
    {arXiv}
    {2020}
    {Approach for curb detection and tracking in urban environments by fusing data from sparse LiDAR, a mono camera, and ultrasonic sensors. Demonstrates over 90\% accuracy in various environments.}
    {https://www.youtube.com/watch?v=w5MwsdWhcy4}{Demo Video 1}
}
\endPublicationList

\startPublicationList
\printPublication{pubAdvancedDriverAssistance}{
  \publication
    {Advanced Driver Assistance Strategies for a Single-Vehicle Overtaking a Platoon on the Two-Lane Two-Way Road}
    {Junjie Chen, Manoj Bhat, Shiyan Jiang, Ding Zhao}
    {IEEE Access}
    {2020}
    {Presents a framework for ADAS tailored for single-vehicle overtaking a platoon on two-lane two-way roads.}
    {https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=9072403}{IEEE Access Link}
}
\endPublicationList

\startPublicationList
\printPublication{pubDiverseTrajectoryForecasting}{
  \publication
    {Diverse and Admissible Trajectory Forecasting through Multimodal Context Understanding}
    {Seong Hyeon Park, Gyubok Lee, Manoj Bhat, Jimin Seo, Minseok Kang, Jonathan Francis, Ashwin Jadhav, Paul Pu Liang, Louis-Philippe Morency}
    {arXiv}
    {2020}
    {Addresses multi-agent trajectory forecasting in autonomous driving by synthesizing multiple input signals.}
    {https://github.com/kami93/CMU-DATF}{Project Repository}
}
\endPublicationList


% \begin{itemize}
% \begin{multicols}{2}
% \publicationItem{\textbf{Advanced Driver Assistance Strategies for a Single-Vehicle Overtaking a Platoon on the Two-Lane Two-Way Road}\\
%     Junjie Chen, Manoj Bhat, Shiyan Jiang, Ding Zhao\\
%     \textit{Conference:} IEEE Access, 2020.\\
%     \textit{Description:} Presents a framework for ADAS tailored for single-vehicle overtaking a platoon on two-lane two-way roads.\\
%     \href{https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=9072403}{IEEE Access Link}}
% \end{multicols}
% \end{itemize}
% \vspace{-10pt}



% \begin{itemize}
% \begin{multicols}{2}
% \publicationItem{
%     \textbf{Density-adaptive Sampling for Heterogeneous Point Cloud Object Segmentation in Autonomous Vehicle Applications}\\
%     Hasan Asy’ari Arief, Mansur Maturidi Arief, Manoj Bhat, Ulf Geir Indahl, Hvard Tveite, Ding Zhao\\
%     \textit{Conference:} Not specified, Year not specified.\\
%     \textit{Description:} Introduces a density-adaptive sampling method to improve classification accuracy in point cloud data for autonomous vehicles.\\
%     \href{}{CVPRW Link}
% }

% \end{multicols}
% \end{itemize}
% \vspace{-10pt}


% \begin{itemize}
% \begin{multicols}{2}
% \publicationItem{
%     \textbf{Diverse and Admissible Trajectory Forecasting through Multimodal Context Understanding}\\
%     Seong Hyeon Park, Gyubok Lee, Manoj Bhat, Jimin Seo, Minseok Kang, Jonathan Francis, Ashwin Jadhav, Paul Pu Liang, Louis-Philippe Morency\\
%     \textit{Conference:} arXiv, 2020.\\
%     \textit{Description:} Addresses multi-agent trajectory forecasting in autonomous driving by synthesizing multiple input signals.\\
%     \href{https://github.com/kami93/CMU-DATF}{Project Repository}
% }
% \end{multicols}
% \end{itemize}
% \vspace{-10pt}


% \begin{itemize}
% \begin{multicols}{2}
% \publicationItem{
%     \textbf{Fast Polar Attentive 3D Object Detection on LiDAR Point Clouds}\\
%     Manoj Bhat, Steve Han, Fatih Porikli\\
%     \textit{Conference:} NeurIPS, 2021.\\
%     \textit{Description:} Introduces a streaming detector for 3D object detection using LiDAR point clouds, emphasizing reduced computational load and latency.\\
%     \href{}{NeurIPS Link}
% }
% \end{multicols}
% \end{itemize}
% \vspace{-10pt}


% \begin{itemize}
% \begin{multicols}{2}
% \publicationItem{
%     \textbf{Smart Annotation and Evaluation Tools for Point Cloud Data}\\
%     Hasan Asy’ari Arief, Mansur Arief, Guilin Zhang, Zuxin Liu, Manoj Bhat, Ulf Geir Indahl, Håvard Tveite, Ding Zhao\\
%     \textit{Conference:} IEEE Access, 2020.\\
%     \textit{Description:} Presents SAnE, a semiautomatic annotation tool for labeling point cloud data, emphasizing high-quality and time-efficient annotation.\\
%     \href{https://ieeexplore.ieee.org/document/9081590}{IEEE Access Link}
% }

% \end{multicols}
% \end{itemize}
% \vspace{-10pt}


% \begin{itemize}
% \begin{multicols}{2}
% \publicationItem{
%     \textbf{Trajformer: Trajectory Prediction with Local Self-Attentive Contexts for Autonomous Driving}\\
%     Manoj Bhat, Jonathan Francis, Jean Oh\\
%     \textit{Conference:} NeurIPS, 2020.\\
%     \textit{Description:} Introduces Trajformer, a self-attention-based encoding structure for improving trajectory prediction in autonomous driving.\\
%     \href{https://github.com/Manojbhat09/Trajformer}{Project Repository}
% }

% \end{multicols}
% \end{itemize}
% \vspace{-10pt}


%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Various Projects at CMU, Safe AI Lab, and Others}}{}
      \resumeItemListStart
        \resumeItem{Developed methodologies for agent trajectory prediction, real-time data processing, and 3D reconstruction.}
        \resumeItem{Participated in competitions and research contributing to advancements in computer vision and machine learning.}
        \resumeItem{Implemented Lane Graphs \& VectorNet focusing on lane association, trajectory prediction, and vehicle behavior.}
        \resumeItem{Worked on state estimation problems (Extended Kalman filter) for tracking the curb and object location using 3D geometry.}
        \resumeItem{Developed and Optimized Neural networks with CRF-CNN for 2D \& 3D Object detection in sensor fused data.}
        \resumeItem{Evaluated PointCNN-XCRF for region proposal and denoising in Segmentation.}
        \resumeItem{Led a team in mechatronics system design for developing a Shipbot robot, focusing on real-time data processing and visual odometry.}
        \resumeItem{Implemented DDPG Reinforcement learning framework with RL-GAN-Net \& PCN for 3D completion and deployed in an annotation tool.}
        \resumeItem{Developed Stereo Imagery based Dense 3D reconstruction and algorithms for vanishing point estimate.}
        \resumeItem{Participated in Kaggle face classification and verification assignment, ranking in the top 5\% of participating teams.}
        \resumeItem{Researched and implemented prototypes for Advanced Driver Assistance Strategies for vehicular overtaking scenarios.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd



%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: C++, Python, Octave, SQL} \\
     \textbf{Frameworks \& Libraries}{: PyTorch, TensorFlow, Keras, ROS, PCL, MongoDB, Redshift, CUDA, OpenGL, Open3D} \\
     \textbf{Tools}{: Git, AWS \& S3, PySpark, Docker, Kubernetes, GDB} \\
     \textbf{Others}{: Deep Learning, Machine Learning, Computer Vision, Robotics}
    }}
 \end{itemize}


\section*{Miscellaneous}
\noindent
\begin{tabularx}{\textwidth}{@{}X r@{}}
\textbf{Reviewer} & ICRA 2022, ICGVIP 2018, CVPR 2022(OmniCV workshop) \\
\textbf{Teaching Assistant} & \\
Digital Image Processing - IIIT-H & July 2016-December 2016 \\
Digital Signal Processing - IIIT-H & January 2017-April 2017 \\
\textbf{Awards} & \\
Dean's Academic Merit List, IIIT-H & November 2014 - November 2017 \\
Dean's Research Merit List, IIIT-H & November 2017 \\
\end{tabularx}


\end{document}
